Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-06 GWLDCII.tex
tweaked the le diagram pictures slightly

% these two for drawing partial propagators
\tikzstyle{firstdash}=[dashed,line cap=round, dash pattern=on 2pt off 1pt]
\tikzstyle{seconddash}=[dashed,line cap=round, dash pattern=on 0.5pt off 1pt]

@@

\begin{figure}
\[
\begin{tikzpicture}[scale = 0.85]
\node at (2.5,5) {\Large $V$};
\node at (12.5,5) {\Large $W$};
\node at (-2,2.5) {\large $n-4 \in I_1^V$};
\node at (-2,-4.5) {\large $n-4 \not\in I_1^V$};
\node at (7.5,2.5) {\Large $\longrightarrow$};
\node at (8,-4.5) {\Large $\longrightarrow$};
% n-4 \in I_1, V
\begin{scope}
\draw[pattern color = gray,pattern = north east lines] (0,4) -- (0,2) -- (2,2) -- (2,4);
\draw[pattern color = gray,pattern = north west lines] (3,4) -- (3,0) -- (4,0) -- (4,4);
\draw (0,0) grid (4,2);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,2) -- (\x,4);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\foreach \c in {(0.5,1.5),(2.5,1.5),(2.5,2.5)} {
  \node at \c {\lezero};
}
\node[red] at (2.5,0.5) {\leplus};
\node at (2.5,3.5) {$\vdots$};
\begin{scope}
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\end{scope}
%\fill[color = white,path fading = south] (0,2) rectangle (6.5,4.1);
\node[below] at (0.5,0) {\tiny $n\vphantom{1}$};
\node[below] at (1.5,0) {\tiny $n-1$};
\node[below] at (2.5,0) {\tiny $n-2$};
\node[below] at (3.5,0) {\tiny $n-3$};
\node[right] at (4,0.5) {\tiny $n-4$};
\node[right] at (4,1.5) {\tiny $n-5$};
\end{scope}

% n-4 \in I_1, W
\begin{scope}[shift = {(9,0)}]
\draw[pattern color = gray,pattern = north east lines] (0,4) -- (0,2) -- (2,2) -- (2,4);
\draw[pattern color = gray,pattern = north west lines] (2,4) -- (2,0) -- (3,0) -- (3,4);
\draw (0,-1) grid (3,2);
\foreach \x in {0,1,2,3} {
  \draw (\x,2) -- (\x,4);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\node[red] at (0.5,1.5) {\leplus};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(-1,0)}]
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\end{scope}
\node[below] at (0.5,-1) {\tiny $n\vphantom{1}$};
\node[below] at (1.5,-1) {\tiny $n-1$};
\node[below] at (2.5,-1) {\tiny $n-2$};
\node[right] at (3,-0.5) {\tiny $n-3$};
\node[right] at (3,0.5) {\tiny $n-4$};
\node[right] at (3,1.5) {\tiny $n-5$};
\end{scope}

% n-4 \not\in I_1, V
\begin{scope}[shift = {(0,-6)}]
\draw[pattern color = gray,pattern = north east lines] (0,3) -- (0,1) -- (2,1) -- (2,3);
\draw[pattern color = gray,pattern = north west lines] (3,3) -- (3,0) -- (4,0) -- (4,3);
\draw (0,0) grid (4,1);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,1) -- (\x,3);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(2.5,1.5)} {
  \node at \c {\lezero};
}
\node at (2.5,2.5) {$\vdots$};
\node[red] at (2.5,0.5) {\leplus};
\begin{scope}[shift = {(1,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (3,4) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\end{scope}

\node[below] at (0.5,0) {\tiny $n\vphantom{1}$};
\node[below] at (1.5,0) {\tiny $n-1$};
\node[below] at (2.5,0) {\tiny $n-2$};
\node[below] at (3.5,0) {\tiny $n-3$};
\node[below] at (4.5,0) {\tiny $n-4$};
\node[right] at (5,0.5) {\tiny $n-5$};
\end{scope}

% n-4 \not\in I_1, W
\begin{scope}[shift = {(9,-6)}]
\draw[pattern color = gray,pattern = north east lines] (0,3) -- (0,1) -- (2,1) -- (2,3);
\draw[pattern color = gray,pattern = north west lines] (2,3) -- (2,0) -- (3,0) -- (3,3);
\draw (0,-1) grid (3,1);
\foreach \x in {0,1,2,3} {
  \draw (\x,1) -- (\x,3);
  };
\node at (0.5,0.5) {\lezero};
\node[red] at (1.5,0.5) {\leplus};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(0,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (3,4) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\end{scope}
\node[below] at (0.5,-1) {\tiny $n\vphantom{1}$};
\node[below] at (1.5,-1) {\tiny $n-1$};
\node[below] at (2.5,-1) {\tiny $n-2$};
\node at (3.5,-0.7) {\tiny $n-3$};
\node at (3.7,-0.2) {\tiny $n-4$};
\node[right] at (4,0.5) {\tiny $n-5$};
\end{scope}
\end{tikzpicture}
\]
\caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}. The shaded regions indicate where the plusses match up perfectly, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
\end{figure}

>>>>

% these two for drawing partial propagators
\tikzstyle{firstdash}=[dashed,line cap=round, dash pattern=on 2pt off 1pt]
\tikzstyle{seconddash}=[dashed,line cap=round, dash pattern=on 0.5pt off 1pt]
\tikzstyle{smalldash}=[dashed,line cap=round, dash pattern=on 1.5pt off 2pt]

@@

\begin{figure}
\[
\begin{tikzpicture}[scale = 0.85]
\node at (2.5,5.5) {\Large $V$};
\node at (12.5,5.5) {\Large $W$};
\node at (-2,2.5) {\large $n-4 \in I_1^V$};
\node at (-2,-4.5) {\large $n-4 \not\in I_1^V$};
\node at (7.5,2.5) {\Large $\longrightarrow$};
\node at (8,-4.5) {\Large $\longrightarrow$};
% n-4 \in I_1, V
\begin{scope}
\fill[pattern color = gray,pattern = north east lines] (0,4.5) -- (0,2) -- (2,2) -- (2,4.5);
\fill[pattern color = gray,pattern = north west lines] (3,4.5) -- (3,0) -- (4,0) -- (4,4.5);
\draw (0,0) grid (4,2);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,2) -- (\x,4);
  \draw[smalldash] (\x,4) -- (\x,4.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\foreach \c in {(0.5,1.5),(2.5,1.5),(2.5,2.5),(2.5,3.3)} {
  \node at \c {\lezero};
}
\node[red] at (2.5,0.5) {\leplus};
\node at (2.5,4.2) {$\vdots$};
\begin{scope}
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (6.6,4.5) -- (4,4.5) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
%\fill[color = white,path fading = south] (0,2) rectangle (6.5,4.1);
\node[below] at (0.5,0) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,0) {\scriptsize $n-1$};
\node[below] at (2.5,0) {\scriptsize $n-2$};
\node[below] at (3.5,0) {\scriptsize $n-3$};
\node[right] at (4,0.5) {\scriptsize $n-4$};
\node[right] at (4,1.5) {\scriptsize $n-5$};
\end{scope}

% n-4 \in I_1, W
\begin{scope}[shift = {(9,0)}]
\fill[pattern color = gray,pattern = north east lines] (0,4.5) -- (0,2) -- (2,2) -- (2,4.5);
\fill[pattern color = gray,pattern = north west lines] (2,4.5) -- (2,0) -- (3,0) -- (3,4.5);
\draw (0,-1) grid (3,2);
\foreach \x in {0,1,2,3} {
  \draw (\x,2) -- (\x,4);
  \draw[smalldash] (\x,4) -- (\x,4.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\node[red] at (0.5,1.5) {\leplus};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(-1,0)}]
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (6.6,4.5) -- (4,4.5) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
\node[below] at (0.5,-1) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,-1) {\scriptsize $n-1$};
\node[below] at (2.5,-1) {\scriptsize $n-2$};
\node[right] at (3,-0.5) {\scriptsize $n-3$};
\node[right] at (3,0.5) {\scriptsize $n-4$};
\node[right] at (3,1.5) {\scriptsize $n-5$};
\end{scope}

% n-4 \not\in I_1, V
\begin{scope}[shift = {(0,-6)}]
\fill[pattern color = gray,pattern = north east lines] (0,3.5) -- (0,1) -- (2,1) -- (2,3.5);
\fill[pattern color = gray,pattern = north west lines] (3,3.5) -- (3,0) -- (4,0) -- (4,3.5);
\draw (0,0) grid (4,1);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,1) -- (\x,3);
    \draw[smalldash] (\x,3) -- (\x,3.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(2.5,1.5),(2.5,2.3)} {
  \node at \c {\lezero};
}
\node[red] at (2.5,0.5) {\leplus};
\node at (2.5,3.2) {$\vdots$};
\begin{scope}[shift = {(1,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4)-- (6.6,4.5) -- (3,4.5) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}

\node[below] at (0.5,0) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,0) {\scriptsize $n-1$};
\node[below] at (2.5,0) {\scriptsize $n-2$};
\node[below] at (3.5,0) {\scriptsize $n-3$};
\node[below] at (4.5,0) {\scriptsize $n-4$};
\node[right] at (5,0.5) {\scriptsize $n-5$};
\end{scope}

% n-4 \not\in I_1, W
\begin{scope}[shift = {(9,-6)}]
\fill[pattern color = gray,pattern = north east lines] (0,3.5) -- (0,1) -- (2,1) -- (2,3.5);
\fill[pattern color = gray,pattern = north west lines] (2,3.5) -- (2,0) -- (3,0) -- (3,3.5);
\draw (0,-1) grid (3,1);
\foreach \x in {0,1,2,3} {
  \draw (\x,1) -- (\x,3);
  \draw[smalldash] (\x,3) -- (\x,3.5);
  };
\node at (0.5,0.5) {\lezero};
\node[red] at (1.5,0.5) {\leplus};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(0,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4)-- (6.6,4.5) -- (3,4.5) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
\node[below] at (0.5,-1) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,-1) {\scriptsize $n-1$};
\node[below] at (2.5,-1) {\scriptsize $n-2$};
\node at (3.5,-0.7) {\scriptsize $n-3$};
\node at (3.7,-0.2) {\scriptsize $n-4$};
\node[right] at (4,0.5) {\scriptsize $n-5$};
\end{scope}
\end{tikzpicture}
\]
\caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}. The shaded regions indicate where the plusses match up perfectly from $V$ to $W$, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
\end{figure}
